Summary Tables

### 2021-07-07 injury_tables.Rmd
Regen removing age and sex in the fatalities' model
Accra, Belohorizonte, Bogota, Cape Town and Sao Paulo results should change because these are the cities where age and sex were removed.

```{r inj_100k = "asis", echo = F, message = F}
require(tibble)
overall_el <- list()
for (city in cities){

@@

@@

  for (cs in names(io[[city]]$outcomes$whw)){
    if (length(names(io[[city]]$outcomes$whw$Baseline)) == 2){
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td3 <- full_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T)) %>% dplyr::select(-c('count.x', 'count.y'))
      #td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

@@

    td4 <- io[[city]]$true_dist %>% filter(stage_mode %in% td3$mode) %>% dplyr::select(stage_mode, cs) %>% as.data.frame()

@@

    td4[, 2] <- as.numeric(td4[,2])

    td4[, 2] <- round((td4[,3] / ( td4[,2] * 365)) * 
                        1000000000, 4)

@@

  }
  print(kable(el, caption = city))

@@

  overall_el[[city]] <- td

}
```

>>>>

```{r inj_100k = "asis", echo = F, message = F}
require(tibble)
overall_el <- list() # To save all cities results
overall_dd <- list() # To save all cities results
for (city in cities){

@@

  el <- list() # To save city specific results

@@

  for (cs in names(io[[city]]$outcomes$whw)){
    if (length(names(io[[city]]$outcomes$whw$Baseline)) == 2){
      # td1: Number of fatalities in nov
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      # td2: Number of fatalities in whw
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      # td3: Number of fatalities: sum of nov and whw
      td3 <- full_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T)) %>% dplyr::select(-c('count.x', 'count.y'))
      #td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

@@

    }
    # td4: distance travelled per mode
    td4 <- io[[city]]$true_dist %>% filter(stage_mode %in% td3$mode) %>% dplyr::select(stage_mode, cs) %>% as.data.frame()

    if (length(el) == 0){
      el <- td4 %>% dplyr::select(stage_mode)
      dd <- el
    }
    # td4: merge total fatalities to distance
    td4 <- full_join(td4, td3 %>% dplyr::select(mode, count) %>% rename(stage_mode = mode), by = 'stage_mode')

@@

    td4[, 2] <- as.numeric(td4[,2])
    # Compute risk per bn km travelled
    td4[, 2] <- round((td4[,3] / ( td4[,2] * 365)) * 
                        1000000000, 4)

@@

    # City's population
    pop <- sum(io[[city]]$demographic$population)
    # Compute distance travelled per capita
    td6 <- td5
    td6[[paste0(var,"_risk")]] <- unlist(td4[2])
    td6[[paste0(var,"_percapita")]] <- td6[[var]] * 365 / pop
    names(td6)[3] <- paste(names(td6)[2], names(td6)[3], sep = "_")
    dd <- full_join(dd, td6, by = 'stage_mode')
  }
  print(kable(el, caption = city))

@@

  overall_el[[city]] <- td
  overall_dd[[city]] <- dd
  cat("\n")
}
```

### 2021-07-07 summary_tables.Rmd
Regen removing age and sex in the fatalities' model
Accra, Belohorizonte, Bogota, Cape Town and Sao Paulo results should change because these are the cities where age and sex were removed.

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 95.8|23.8|1.7 |
| cycle | 0.6|0.5|0.2 |
| car | 0.8|16.3|20.6 |
| motorcycle | 0.0|0.0|3.1 |
| bus | 2.4|47.2|62.9 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 65.5|21.2|1.3 |
| cycle | 2.0|8.7|1.0 |
| car | 1.1|4.0|5.8 |
| motorcycle | 5.8|31.7|54.0 |
| bus | 23.9|30.6|34.6 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.1|8.6|0.3 |
| cycle | 1.6|2.7|0.2 |
| car | 7.3|65.1|43.9 |
| motorcycle | 1.3|10.1|5.0 |
| bus | 0.4|11.0|40.1 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 91.0|20.9|1.2 |
| cycle | 4.8|12.0|2.0 |
| car | 1.5|26.6|29.2 |
| motorcycle | 0.5|5.9|6.5 |
| bus | 0.8|20.6|56.7 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 80.1|2.9|0.1 |
| cycle | 7.4|3.6|0.3 |
| car | 6.2|34.4|21.2 |
| motorcycle | 0.6|2.8|1.2 |
| bus | 3.5|50.0|50.7 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|5.3|1.9 |
| cycle | 0.2|0.5|0.1 |
| car | 8.0|55.5|48.1 |
| motorcycle | 0.0|0.7|0.4 |
| bus | 6.9|34.8|33.1 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.9|3.5|0.0 |
| cycle | 2.4|3.2|0.2 |
| car | 2.2|37.9|31.8 |
| motorcycle | 0.4|3.2|0.9 |
| bus | 1.7|34.8|33.8 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|3.9|0.0 |
| cycle | 6.2|6.1|0.5 |
| car | 8.1|58.7|32.3 |
| motorcycle | 0.1|2.2|1.1 |
| bus | 0.5|20.5|28.7 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 82.6|1.9|0.0 |
| cycle | 1.3|1.4|0.1 |
| car | 12.6|65.2|36.8 |
| motorcycle | 0.8|3.1|1.9 |
| bus | 1.0|21.3|28.8 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 86.1|19.6|0.1 |
| cycle | 2.6|6.6|2.0 |
| car | 0.6|2.4|2.8 |
| motorcycle | 6.9|24.1|24.3 |
| bus | 0.8|26.7|54.8 |

>>>>

|accra|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 95.8|23.8|1.7 |
| cycle | 0.6|0.5|0.2 |
| car | 0.8|16.3|20.6 |
| motorcycle | 0.0|0.0|3.1 |
| bus | 2.5|47.4|63.1 |

|bangalore|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 65.5|21.2|1.3 |
| cycle | 2.0|8.7|1.0 |
| car | 1.1|4.0|5.8 |
| motorcycle | 5.8|31.7|54.0 |
| bus | 24.0|30.6|34.7 |

|belo_horizonte|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 89.1|8.6|0.3 |
| cycle | 1.6|2.7|0.2 |
| car | 7.3|65.1|43.9 |
| motorcycle | 1.3|10.1|5.0 |
| bus | 0.4|11.0|43.5 |

|bogota|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 91.0|20.9|1.2 |
| cycle | 4.8|12.0|2.0 |
| car | 1.5|26.6|29.2 |
| motorcycle | 0.5|5.9|6.5 |
| bus | 0.8|20.6|56.7 |

|buenos_aires|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 80.1|2.9|0.1 |
| cycle | 7.4|3.6|0.3 |
| car | 6.2|34.4|21.2 |
| motorcycle | 0.6|2.8|1.2 |
| bus | 3.5|51.0|75.9 |

|cape_town|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|5.3|1.9 |
| cycle | 0.2|0.5|0.1 |
| car | 8.0|55.5|48.1 |
| motorcycle | 0.0|0.7|0.4 |
| bus | 7.5|37.9|49.0 |

|delhi|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 84.4|10.1|0.9 |
| cycle | 2.0|7.6|3.7 |
| car | 2.4|17.3|21.4 |
| motorcycle | 5.6|30.1|26.5 |
| bus | 0.8|25.0|40.9 |

|mexico_city|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 89.9|3.5|0.0 |
| cycle | 2.4|3.2|0.2 |
| car | 2.2|37.9|31.8 |
| motorcycle | 0.4|3.2|0.9 |
| bus | 1.8|35.3|64.7 |

|santiago|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|3.9|0.0 |
| cycle | 6.2|6.1|0.5 |
| car | 8.1|58.7|32.3 |
| motorcycle | 0.1|2.2|1.1 |
| bus | 0.6|21.8|64.6 |

|sao_paulo|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 82.6|1.9|0.0 |
| cycle | 1.3|1.4|0.1 |
| car | 12.6|65.2|36.8 |
| motorcycle | 0.8|3.1|1.9 |
| bus | 1.0|22.0|59.7 |

|vizag|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 86.1|19.6|0.1 |
| cycle | 2.6|6.6|2.0 |
| car | 0.6|2.4|2.8 |
| motorcycle | 6.9|24.1|24.3 |
| bus | 0.8|26.7|54.8 |
